\documentclass{rpt}

\title{Weekly Report}
\author{}
\date{\today}

\begin{document}

\maketitle

\section{Targets}

\subsection{Urgent}
\begin{itemize}
    \item Randomly selecting a node,
        compute its care set,
        change its care set,
        synthesize the local circuit,
        evaluate its area and error rate,
        accept it with a certain probability.
\end{itemize}

\subsection{Important}
\begin{itemize}
    \item Use model counting to compute error rate, i.e., how many assignments satisfying a SAT problem.
    \item Use approximate confidence interval / hypothesis testing of Bernoulli experiments to evaluate the accuracy of error rate.
    \item Trade off the accuracy of batch error estimation for speed
        (even directly use Su's equation to update Boolean difference),
        perhaps use hypothesis testing to evaluate the accuracy.
    \item Combine the simulation of circuits with the simulation of Monte Carlo Tree Search.
        In other words,
        in one loop of Monte Carlo Tree Search,
        merge logic simulation and playout (only simulate circuit once and playout once).
    \item Represent circuit with AIG because of more potential LAC candidates.
        For each round, select one or more input wires and replace them with constant 0 or 1.
        Consider how to combine Wu's method (choose a subset of input wires and substitute).
    \item Accelerate Approximate Logic Synthesis Ordered by Monte Carlo Tree Search:
        reuse the result of batch error estimation in playout.
    \item How DC affects BDD
    \item Induce DC with PLA files
\end{itemize}

\subsection{Worth Trying}
\begin{itemize}
    \item Enhance default policy with greedy approach or field domain knowledge.
    \item In expansion process of MCTS, expand more than one layers.
    \item Tune parameters in MCTS\@.
    \item Perform greedy flow on leaves of the final Monte Carlo Search Tree.
    \item Combine beam search and MCTS\@.
\end{itemize}

\subsection{Potential Topics}
\begin{itemize}
    \item Relationship between power simulation and logic simulation.
    \item Combine Binarized Neural Network with approximate computing.
    \item Relationship between Boolean network and Bayesian Network.
    \item Approximate TMR\@.
\end{itemize}

\section{Progress}

To implement
\[
    \mathbf{\hat{y}} = (\hat{f}_1(\mathbf{x}), \ldots, \hat{f}_O(\mathbf{x})),
\]
where
\[
    \hat{f}_i(\mathbf{x}) = f_i(\mathbf{x})|_{\mathbf{x} = \mathbf{a}_1} \lor \ldots \lor f_i(\mathbf{x})|_{\mathbf{x} = \mathbf{a}_R}
\]
I did 2 experiments.

\subsection{Experiment 1}
Directly build the level circuit according to its SOP expression,
and synthesize it with the script ``resyn2''.

For c880, original area is 607,
when $R=100$, approximate circuit has an area of 3324.
It is impractical,
since it seems hard for the multi-level synthesis tool to simplify a 2-level SOP expression circuit.

\subsection{Experiment 2}
Let $\mathbf{A} = [\mathbf{a}_1, \ldots, \mathbf{a}_R]$ be the care set.
Simplify the windows $\mathbb{W}$ with the care set.

Also for c880,

\begin{tabular}{ccc}
    \hline
    $R$ & area & ER \\
    \hline
    100 & 526 & 0.11104 \\
    \hline
    200 & 539 & 0.024631 \\
    \hline
    206 & 539 & 0.024631 \\
    \hline
    212 & 542 & 0.004503 \\
    \hline
    225 & 542 & 0.004503 \\
    \hline
    250 & 542 & 0.004503 \\
    \hline
    300 & 543 & 0.004503 \\
    \hline
    500 & 554 & 0.003345 \\
    \hline
    1000 & 553 & 0.000701 \\
    \hline
\end{tabular}

For c1908,

\begin{tabular}{ccc}
    \hline
    $R$ & area & ER \\
    \hline
    100 & 374 &  0.082238 \\
    \hline
    1000 & 567 & 0.028422 \\
    \hline
    2000 & 625 & 0.008439 \\ 
    \hline
    2500 & 657 & 0.000369 \\
\end{tabular}

When $ER$ is small, similar result compared with Su-TCAD is generated.
But $ER$ changes abruptly near $R=210$.

Reason of great change might be:
\begin{itemize}
    \item
        I use interpolation method to simplify the circuit.
        Sometimes when care set changes,
        interpolation does not change.
    \item
        I directly change the care set of primary input.
        Slightly change on PIs may cause large disturbance.
        Maybe partial change will work more elaborately.
\end{itemize}

\end{document}
